PANCHANGE_data_preprocessing

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed startDate.glad to startDate.prepandemic

# Select variables
```{r glad dem cleaning}
if(GLAD == TRUE){
exclude_cols_dem <- c("ID",
                  "Sample",
                  "startDate.glad",
                  "Age_uncleaned",
                  "EduYrs")

glad.dem.raw.id <- glad.dem.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
         Sample, # Sample
         ID, # ID
         startDate.glad, #Date when participant signed up to glad
         Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
         Gender = demographics.which_gender_do_you_identify_with, # Gender
         Sex = demographics.select_questionnaire_items_medical, #Sex
         EduYrs = demographics.school_education_school_years.txt, # Years in education
         demographics.college_or_university_degree, # level of education - univeristy
         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
         demographics.cses_or_equivalent, # level of education - cse
         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
         ) %>%
  add_numeric(., exclude = exclude_cols_dem) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

# NBR demographics

## Read in data
```{r nbr dem cols}
if(NBR == TRUE){
  nbr.dem.raw <- readRDS(file = paste0(data.raw_path, "/nbr/dem_nbr.rds"))
  dim(nbr.dem.raw)
  colnames(nbr.dem.raw)
}
```

@@

glad.gad.raw.id <- glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad mhd cleaning}
glad.mhd.raw.id <- glad.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad pcl cleaning}
glad.pcl.raw.id <- glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
    pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_prepan = pcl.difficulty_concentrating
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad phq cleaning}
glad.phq.raw.id <- glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
    phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad ocir cleaning}
glad.ocir.raw.id <- glad.ocir.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
    ocir.arranged_things_prepan = ocir.arranged_things,
    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
    ocir.saved_things_prepan = ocir.saved_things,
    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping glad gad cleaning}
exclude_cols_coping_glad <- c(
  "Sample",
  "ID",
  "startDate.coping.glad"
)

>>>>

# Select variables
```{r glad dem cleaning}
if(GLAD == TRUE){
exclude_cols_dem <- c("ID",
                  "Sample",
                  "startDate.prepandemic",
                  "Age_uncleaned",
                  "EduYrs")

glad.dem.raw.id <- glad.dem.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
         Sample, # Sample
         ID, # ID
         startDate.prepandemic, #Date when participant signed up to glad
         Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
         Gender = demographics.which_gender_do_you_identify_with, # Gender
         Sex = demographics.select_questionnaire_items_medical, #Sex
         EduYrs = demographics.school_education_school_years.txt, # Years in education
         demographics.college_or_university_degree, # level of education - univeristy
         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
         demographics.cses_or_equivalent, # level of education - cse
         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
         ) %>%
  add_numeric(., exclude = exclude_cols_dem) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad copy dem}
if(GLAD == TRUE){
dem.raw.id <- glad.dem.raw.id
}
```

# EDGI demographics
## Read in data
```{r edgi dem cols}
if(EDGI == TRUE){
  edgi.dem.raw <- readRDS(file = paste0(data.raw_path, "/edgi/dem_edgi.rds"))
  dim(edgi.dem.raw)
  colnames(edgi.dem.raw)
}
```

# Select variables
```{r edgi dem cleaning}
if(EDGI == TRUE){
  exclude_cols_dem <- c("ID",
                        "Sample",
                        "startDate.edgi",
                        "Age_uncleaned",
                        "EduYrs")

  edgi.dem.raw.id <- edgi.dem.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID),
           startDate.edgi = startDate) %>% # Rename startDate
    select(
      Sample, # Sample
      ID, # ID
      startDate.edgi, #Date when participant signed up to edgi
      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
      Gender = demographics.which_gender_do_you_identify_with, # Gender
      Sex = demographics.select_questionnaire_items_medical, #Sex
      EduYrs = demographics.school_education_school_years.txt, # Years in education
      demographics.college_or_university_degree, # level of education - univeristy
      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
      demographics.cses_or_equivalent, # level of education - cse
      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
    ) %>%
    add_numeric(., exclude = exclude_cols_dem) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

  # Inspect dimensions
  dim(edgi.dem.raw.id)
  # Inspect colnames
  colnames(edgi.dem.raw.id)
  #Differences
  dim(edgi.dem.raw)[1]-dim(edgi.dem.raw.id)[1]
}
```

```{r edgi copy dem}
if(EDGI == TRUE){
  dem.raw.id <- edgi.dem.raw.id
}
```

# NBR demographics
## Read in data
```{r nbr dem cols}
if(NBR == TRUE){
  nbr.dem.raw <- readRDS(file = paste0(data.raw_path, "/nbr/dem_nbr.rds"))
  dim(nbr.dem.raw)
  colnames(nbr.dem.raw)
}
```

@@

glad.gad.raw.id <- glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad mhd cleaning}
glad.mhd.raw.id <- glad.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad pcl cleaning}
glad.pcl.raw.id <- glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
    pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_prepan = pcl.difficulty_concentrating
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad phq cleaning}
glad.phq.raw.id <- glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
    phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r glad ocir cleaning}
glad.ocir.raw.id <- glad.ocir.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
    ocir.arranged_things_prepan = ocir.arranged_things,
    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
    ocir.saved_things_prepan = ocir.saved_things,
    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping glad gad cleaning}
exclude_cols_coping_glad <- c(
  "Sample",
  "ID",
  "startDate.coping"
)

coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping.glad = startDate,
    gad.problems_made_difficult_care, # Impairment
    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad.trouble_relaxing,
    gad.sit_restless_hard_retro = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
  ) %>%
  add_numeric(., exclude = exclude_cols_coping_glad) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
